
\noindent
\begin{flushright}
\huge List of Related Publications
\end{flushright} 
\vspace{50pt} 

%The work described in this thesis has appeared in the following publications: \\
%\vspace{24pt} 
\hangindent=1.5cm \textbf{Papon, J.};  Wörgötter, F., ``{Spatially Stratified Correspondence Sampling for Real-Time Point Cloud Tracking,}'' \emph{Applications of Computer Vision (WACV), 2015 IEEE International Conference on}, Jan. 2015. \\
\vspace{6pt}

\hangindent=1.5cm \textbf{Papon, J.};  Kulvicius, T.; Aksoy, E.; Wörgötter, F., ``\href{http://www.dpi.physik.uni-goettingen.de/cns/uploads_bibtexmodule/PDF/paponkulviciusaksoy2013.pdf}{Point Cloud Video Object Segmentation using a Persistent Supervoxel World-Model,}'' \emph{Intelligent Robots and Systems (IROS), 2013 IEEE/RSJ International Conference on}, Nov. 2013. \\
\vspace{6pt}

\hangindent=1.5cm \textbf{Papon, J.};  Abramov, A.; Schoeler, M.; Wörgötter, F., ``\href{http://www.cv-foundation.org/openaccess/content_cvpr_2013/papers/Papon_Voxel_Cloud_Connectivity_2013_CVPR_paper.pdf}{Voxel Cloud Connectivity Segmentation - Supervoxels for Point Clouds,}'' \emph{Computer Vision and Pattern Recognition (CVPR) 2013}, June 2013. \\
\vspace{6pt}

\hangindent=1.5cm \textbf{Papon, J.};  Abramov, A.; Wörgötter, F., ``\href{http://dx.doi.org/10.1007/978-3-642-33885-4_24}{Occlusion Handling in Video Segmentation via Predictive Feedback,}'' \emph{European Conference on Computer Vision (ECCV) 2012}. Workshops and Demonstrations, Lecture Notes in Computer Science Volume 7585, 2012, pp 233-242. \\
\vspace{6pt}

\hangindent=1.5cm \textbf{Papon, J.};  Abramov, A.; Aksoy, E.; Wörgötter, F., ``\href{http://dx.doi.org/10.1109/WACV.2012.6163002}{A modular system architecture for online parallel vision pipelines,}'' \emph{Applications of Computer Vision (WACV) 2012}, pp.361-368, Jan. 2012. \\
\vspace{6pt}

\hangindent=1.5cm Stein, S.; Schoeler, M.; \textbf{Papon, J.};  Wörgötter, F., ``\href{http://www.cv-foundation.org/openaccess/content_cvpr_2014/html/Stein_Object_Partitioning_using_2014_CVPR_paper.html}{Object Partitioning using Local Convexity,}'' \emph{Computer Vision and Pattern Recognition (CVPR) 2014}, June 2014. \\
\vspace{6pt}

\hangindent=1.5cm Stein, S.;  Wörgötter, F.; Schoeler, M.; \textbf{Papon, J.}; Kulvicius, T., ``\href{http://www.dpi.physik.uni-goettingen.de/cns/modules/BibtexModule/uploads/PDF/steinwoergoetterschoeler2014.pdf}{Convexity Based Object Partitioning For Robot Applications,}'' \emph{Robotics and Automation (ICRA), 2014 IEEE/RSJ International Conference on}, June 2014. \\
\vspace{6pt}

\hangindent=1.5cm Schlette, C.; Buch, A.; Aksoy, E.; Steil, T.; \textbf{Papon, J.}; Savarimuthu, T.R.; Wörgötter, F.; Krüger, N.; Roßmann, J., ``\href{http://link.springer.com/article/10.1007/s11740-014-0552-0}{A new benchmark for pose estimation with ground truth from virtual reality,}'' \emph{Production Engineering}, May 2014. \\
\vspace{6pt}

\hangindent=1.5cm Aein, M.J.;  Aksoy, E.; Tamosuinaite, M.; \textbf{Papon, J.}; Ude, A.; Wörgötter, F., ``\href{http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6697011&tag=1}{
Toward a library of manipulation actions based on semantic object-action relations,}'' \emph{Intelligent Robots and Systems (IROS), 2013 IEEE/RSJ International Conference on}, Nov. 2013.\\
\vspace{6pt}

\hangindent=1.5cm Abramov, A.; Pauwels, K.; \textbf{Papon, J.}; Wörgötter, F.; Dellen, B., ``\href{http://dx.doi.org/10.1109/WACV.2012.6163000}{Depth-supported real-time video segmentation with the Kinect,}'' \emph{Applications of Computer Vision (WACV) 2012}, Jan. 2012.\\
\vspace{100pt}

The research leading to this thesis was supported with funding from the European Community's Seventh Framework Programme FP7/2007-2013 (Specific Programme Cooperation, Theme 3, Information and Communication Technologies) under grant agreement no. 270273, Xperience and grant agreement no. 269959, IntellAct.

 
