% the acknowledgments section
\begin{savequote}[75mm]
\onehalfspacing
\textnormal{``Le seul v\'{e}ritable voyage, ce ne serait pas d'aller vers de nouveaux paysages, mais d'avoir d'autres yeux, de voir l'univers avec les yeux d'un autre, de cent autres, de voir les cent univers que chacun d'eux voit, que chacun d'eux est.''} 

\vspace{16pt} 

\textit{The only true voyage, would not be a journey towards new landscapes, but to possess new eyes, to see the universe through the eyes of another, of a hundred others, to behold the hundred universes that each of them sees, that each of them is.}
\qauthor{Marcel Proust}
\end{savequote}

\chapter*{Acknowledgments}
\vspace{40mm}
\newthought{I would never have made it through} to the end of this thesis without the support of my friends, family, and colleagues. I'd like to thank my supervisors Prof. Dr. Florentin W\"org\"otter and Prof. Dr. Dieter Hogrefe for their guidance, aid, and many fruitful discussions which helped bring about this work. Special thanks go out to our close-knit (talkative) vision group: Dr. Eren Erdal Aksoy, Simon Reich, Simon Stein, and Markus Sch\"oler. I'd also like to thank our robot-men Dr. Tomas Kulvicius and Mohamad Javad Aein for all their hard work making it work (usually) in the real-world. I also would like to thank all of my friends and colleagues up at the University of Southern Denmark, as well as all the IntellAct partners with whom I had the good fortune of passing so much time in Odense. 
\vspace{20pt}
A heart-felt thanks to all of the members of Florentin's group, which has become my extended family in Germany. It's been a pleasure working and living with all of you: Mohamad Javad Aein, Dr. Alejandro Agostini, Martin Biehl, Jan-Matthias Braun, Sakyasingha Dasgupta, Michael Fauth, Dennis Goldschmidt, Dr. Yinyun Li, Timo Nachstedt, Dr. Poramate Manoonpong, Dr. Minija Tamosiunaite, Dr. Christian Tetzlaff, and Xiaofeng Xiong. An especially big thanks to Ursula Hahn-W\"org\"otter for putting up with me and being such a big help in figuring out Germany.
\vspace{20pt}
Last (but far from least) I want to thank my family. I could have never made it here without the unwavering support of my father, Jean-Marc, and my mother, Marian. I thank them especially for hosting me every Summer in Veyssou and on the boat - time away from work that proved invaluable. I know at times I was a handful to deal with (perhaps a few handfuls), and your constant love and support were instrumental in seeing me through. Of course I would also like to thank my loving sister Camille, who, even half a world away, hasn't forgotten her little brother.
\begin{flushright}
\vspace{20pt}
Thank you all, so very, very much! \\
\vspace{20pt}
\textsc{J\'er\'emie Papon} \\
\textsc{G\"ottingen, 2014.}
\end{flushright}

